\documentclass[0main.tex]{subfiles}
\graphicspath{{./img}}
\begin{document}
\section{Discussion}

This section goes over the overall process the work that has been done regarding the thesis
and evaluate the outcomes.  Firstly, it should be assessed whether the thesis has fulfilled the
given guidelines in the thesis assignment. The following section goes over the guidelines
and discuss whether the assignment outline has been fulfilled. 

\ul{\textbf{Research question \#1:} Can agent-based modeling be applied to simulate ITS in
vehicle simulators and are they a viable option?}

In section \ref{sec-mas}, the literature regarding Multi-agent Systems is reviewed. The review
is focused mainly on the primary characteristics of MAS and on various types and implementation
methodologies of MAS. The outcome of the section is identifying important implementation
details of MAS which would aid in ITS implementation using agent-based modelling. 

In section \ref{sec-its}, the current research regarding ITS systems is reviewed. The current
trends in ITS suggest that modern ITS systems will rely on maximizing interoperability between
individual road users, utilizing direct, non-centralized wireless communication. Such features
are common in agent-based systems as well, therefore it has been concluded that MAS could
represent a convenient way how to simulate such systems. Cooperative ITS (C-ITS) systems and
connected In-vehicle Information Systems are identified as the most suitable systems for
application using MAS.

\ul{\textbf{Research question \#2:} How would an ITS simulation be implemented into an existing
IVS using agent-based modelling?}

In section \ref{sec-system}, a system to integrate novel ITS solutions into a vehicle simulator
is developed using the research findings in the preceding parts of the thesis. The system
implemented the \textsubscript{3}T architecture for individual agents that is supposed to
offer a sufficient balance between system complexity and modularity. The architecture of the
macro-system, which defined mainly how agents interact with each other, is also developed
in line with requirements based on MAS research as well. The system is then implemented using
the C\# programming language, because of its object-oriented properties and the fact that the
intended simulator software uses C\# scripting API as well, allowing for deep integration with
the software. The implementation comprises partially functional classes that define the
system's structure but are open to detailed logic implementation based on a specific use
case. 

\ul{\textbf{Research question \#3:} What are the available modules and libraries for
implementing MAS in different programming languages? }

As a secondary objective to building an ITS simulation framework for an IVS, it is required to
review available MAS implementation modules that would facilitate building the desired
framework. Multiple modules are reviewed, including their main use-cases and implementation
details. After discussing the main aspects of integration into the simulator software (section
\ref{sec-toolset}), it is concluded that there are no suitable modules for MAS implementation
to the specific IVS, as the researched modules are either outdated or focused on different
aspects of multi-agent systems. Therefore, it is decided that the framework would be built
from the ground up.

\ul{\textbf{Research question \#4:} What are the advantages and challenges associated with
using agent-based modeling to simulate Intelligent Transport Systems in vehicle simulators, and
how can they be addressed?}

The system evaluation is, in part, done by implementing a sample C-ITS system into the
simulator software, with a cooperative traffic light and connected vehicles. The implementation
of the sample system proves that it is possible to implement specific ITS solutions using
the developed framework, therefore simulating Intelligent Transport Systems using agent-based
modeling is possible.

The observed challenges are that implementing conflict resolution and cooperation between
agents deems to be a very complex topic which would take a lot of additional research and
effort to implement and therefore is decided that it will not be part of the developed ITS
implementation framework. This could result in a less stable agent behaviour during simulation.
This missing feature could be added in future improvements to the framework.

\subsection{Results}

Based on the designed system and its implementation, the implications of the research activity
and its benefits, caveats and application possibilities are analyzed. 

\subsubsection{Benefits}

The main benefit of developing an ITS implementation framework is obvious. In theory,
the framework should facilitate ITS implementation into a vehicle simulator so that it enables
the developer to focus more on the high-level implementation related to the ITS system itself,
as the structure of the underlying agent system would be pre-implemented. 

For instance, the developer implementing a given ITS solution into the IVS can implement a
desired behavior of an actor in the system by dividing the algorithm into atomical skill
modules which inherently makes developing complex behavior easier and more manageable, as well
as open to extending its capabilities by iteratively adding more modules. Also, one of the
greater benefits is the fact that communication API  for the system developer has been
implemented, according to the C-ITS ETSI standards. This makes it very easy for developers to
implement C-ITS systems which rely heavily on distributed road user communication, which has
been the case when developing a sample ITS simulation (dynamic vehicle navigation) in order to
validate the framework's capabilities. The development process of the communication interface
was simply filling the pre-defined DENM and CAM message parameters with desired information.
The inner architecture of agents defined by the framework allows to develop complex, dynamic
behaviour.

\subsubsection{Shortcomings}

When implementing the sample C-ITS system using the proposed framework, shortcomings were also
identified during the process. The perceived disadvantage of using the framework is that when
implementing a simple behavior that does not need complex decision-making, all the agent layers
need to be implemented, although they might not be fully utilized. For instance, the
\emph{Connected traffic light} in section \ref{sec-implementation} only has one goal in the
deliberation layer and also just one task to perform, which implies that the agent model could
have been reduced just to a static, cyclic execution of the skills used mainly for
communication with the connected vehicles. Therefore, the developed MAS framework is likely to
demonstrate its advantages only when building larger-scale ITS projects in the vehicle
simulator which require developing complex behavior logic for the agents. 

Another potential disadvantage that was identified during the framework development is that
although the 3-layer concept might be effective, it might not be intuitive to use for someone
new to the concepts for multi-agent systems. For instance, it is not very clear how to decide
on the atomicity of the individual actions the agent can perform. However, this problem can be
solved by providing a template for a "simple" agent which has got the deliberation (and
potentially also the middle sequencing layer) in a single state. 

\subsection{Future work and implications}

Regarding future work and further improvements of the outcomes of this thesis, it would be
beneficial to implement agent negotiation, which has been discussed in the theoretical part of
the thesis but has not been implemented as part of the framework. The system validation section
has shown that it is possible to develop fully functional simulations of Intelligent Transport
Systems, however, developing a negotiation model for the agents would make the framework more
robust and would allow modeling systems with greater complexity.

Apart from the improvement mentioned above, the system can already be used to model ITS systems
with intelligent agents, including state-of-the-art cooperative ITS systems. To mention a few,
the framework can model various in-vehicle information systems, such as the intersection
collision warning, emergency vehicle warning or overtaking warning. Apart from the mentioned
sensing \& perception systems, planning-focused its systems such as dynamic vehicle routing or
green light optimal speed advisory can be modeled. After the potential improvement of adding
agent negotiation, it would also be possible to implement autonomous driving and related
advanced driver assistance systems using the framework.

\end{document}