\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{cm-super}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{svg}
\usepackage[a4paper, top=25mm, bottom=25mm, left=30mm, right=20mm, twoside]{geometry}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[sorting=none]{biblatex} 
\usepackage{color}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{subfiles}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{soul}

\title{blank}
\author{Jan Macek}
\date{May 2023}

\begin{document}

\vspace*{\fill}

{\large\bfseries Statutory Declaration}\bigskip

I, Jan Macek, solemnly and sincerely declare that:

I am the author of the master's thesis titled \emph{Agent-based Modeling of ITS Systems in Vehicle
Simulator}.

The research work presented in this thesis is the result of my own original investigations,
except where otherwise acknowledged.

I have appropriately acknowledged and referenced all sources used in this thesis, including but
not limited to published and unpublished works, data, and other materials, in accordance with
the recognized academic standards and conventions.

I have clearly identified and cited the contributions of others to my research, including
collaborators, advisors, and previous researchers, through appropriate acknowledgment and
citation in the relevant sections of this thesis.

I have not engaged in any form of academic misconduct, including plagiarism, fabrication,
falsification, or any other fraudulent practices, in the preparation or presentation of this
thesis.

This thesis has not been submitted, in whole or in part, for the award of any other degree,
diploma, or qualification.

I have adhered to the ethical guidelines and principles governing research involving human
subjects, and I have obtained the necessary ethical clearances and permissions, where
applicable, prior to conducting any research involving human participants.

I understand that any violation of the above declarations may result in severe consequences,
including the cancellation of my degree and other disciplinary actions as deemed appropriate by
the academic institution.

I make this solemn declaration conscientiously, believing it to be true and knowing that it is
of the same legal force and effect as if made under oath.\bigskip

\hspace*{\fill}\emph{Signed:}\hspace{5cm}

\vspace{3cm}
\end{document}
